Detailed disease progression of 88 patients hospitalized with Covid-19 in the Czech Republic: A dataset and exploratory analysis

### 2020-09-12 dev/raw_data_preprocessing.Rmd
First working stan_jm models

```{r}
for(n in names(anonymized_data) ) {
  write_csv(anonymized_data[[n]], path = here::here("private_data", paste0(n,".csv")))
}
```

>>>>

```{r}
for(n in names(anonymized_data) ) {
  write_csv(anonymized_data[[n]], path = here::here("private_data", paste0(n,".csv")))
}
write_lines(digest::digest(anonymized_data), path = here::here("private_data", "data_revision.txt"))
```

### 2020-09-12 manuscript/jm.Rmd
First working stan_jm models

```{r, setup}
devtools::load_all()
library(tidyverse)
library(survival)
library(rstanarm)

@@

@@

data_surv <- wide %>%  
  filter(day > 0) %>%
  mutate(daym1 = day - 1,
    status = fct_collapse(breathing, Hospitalized = breathing_levels) %>% factor(ordered = FALSE) %>% fct_relevel("Hospitalized", "Discharged", "Death") %>% fct_explicit_na("Hospitalized")
  ) %>%
  inner_join(data$patient_data, by = c("hospital_id", "patient_id"))

tt <- stan_jm(formulaLong = CRP ~ day + (1 | patient_id),
              dataLong = wide,
              formulaEvent = Surv(daym1, day,status) ~ age + sex + took_hcq,
              dataEvent = data_surv,
              id_var = "patient_id",
              time_var = "day")
```

>>>>

```{r setup}
devtools::load_all()
library(tidyverse)
library(survival)
library(rstanarm)

@@

options(mc.cores = parallel::detectCores())

@@

data_surv <- wide %>%  
  filter(day > 0) %>%
  mutate(daym1 = day - 1,
    event_death = !is.na(breathing) & breathing == "Death",
    event_discharged = !is.na(breathing) & breathing == "Discharged",
  ) %>%
  inner_join(data$patient_data, by = c("hospital_id", "patient_id"))  %>%
  arrange("patient_id", "day")

#TODO: impute the competing risk as censored long in the future
```

```{r}
data_d_dimer <- data_surv %>%
  group_by(patient_id) %>%
  filter(any(!is.na(d_dimer))) %>%
  ungroup() %>%
    select(event_death, event_discharged, 
         day, daym1, patient_id, hospital_id, 
         age, sex, took_hcq,
         d_dimer) %>%
  mutate(log_d_dimer = log(d_dimer + 1) - 4)

data_d_dimer %>% filter(d_dimer == 0)
# data_d_dimer %>% group_by(sex, ever_hcq) %>% summarise(pts = length(unique(patient_id)), n_dimer = sum(!is.na(d_dimer)))

fit_d_dimer_age_sex_hcq <- stan_jm_with_cache(formulaLong = log_d_dimer ~ day + (1  | patient_id),
              dataLong = data_d_dimer %>% filter(!is.na(d_dimer)),
              formulaEvent = Surv(daym1, day, event_death) ~ age + sex + took_hcq,
              dataEvent = data_d_dimer,
              id_var = "patient_id",
              time_var = "day",
              cache_file = paste0(cache_dir, "/jm_d_dimer_age_sex_hcq.rds"))

fit_d_dimer_age_sex_hcq

#length(unique(data_d_dimer$patient_id))
to_pred <- data_d_dimer %>% group_by(patient_id) %>% summarise(n_d_dimer = sum(!is.na(d_dimer))) %>%
  filter(n_d_dimer > 1) %>% pull(patient_id)
#data_d_dimer %>% filter(patient_id == unique(data_d_dimer$patient_id)[31])

```
```{r}
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[1:11])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[12:14])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[15:18])
plot(p1, plot_observed = TRUE)

p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[19:20])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[21:22])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[22:26])
plot(p1, plot_observed = TRUE)
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[27:29])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[30:32])
plot(p1, plot_observed = TRUE)                     
```

```{r}
data_IL_6 <- data_surv %>%
  group_by(patient_id) %>%
  filter(any(!is.na(IL_6))) %>%
  ungroup() %>% 
  select(event_death, event_discharged, 
         day, daym1, patient_id, hospital_id, 
         age, sex, took_hcq,
         IL_6) %>%
  mutate(log_IL_6 = log(IL_6))

fit_IL_6_age_sex_hcq <- stan_jm_with_cache(formulaLong = log_IL_6 ~ day + (1 + day | patient_id),
              dataLong = data_IL_6 %>% filter(!is.na(IL_6)),
              formulaEvent = Surv(daym1, day, event_death) ~ age + sex + took_hcq,
              dataEvent = data_IL_6,
              id_var = "patient_id",
              time_var = "day",
              cache_file = paste0(cache_dir, "/jm_IL_6_age_sex_hcq.rds"))

fit_IL_6_age_sex_hcq

```
```{r}
for(id in unique(data_IL_6$patient_id)) {
  p1 <- posterior_traj(fit_IL_6_age_sex_hcq, ids = id)
  print(plot(p1, plot_observed = TRUE)                     )
}

### 2020-09-12 manuscript/manuscript.Rmd
First working stan_jm models

```
{r setup}
devtools::load_all()
library(tidyverse)
theme_set(cowplot::theme_cowplot())
data <- read_data_for_analysis()
```

@@

```
{r}
n_patients <- nrow(data$patient_data)
n_hospitals <- length(unique(data$patient_data$hospital_id))
```

>>>>

```{r setup}
devtools::load_all()
library(tidyverse)
theme_set(cowplot::theme_cowplot())
data <- read_data_for_analysis()
wide <- prepare_marker_data_wide(data)
```

@@

```{r}
n_patients <- nrow(data$patient_data)
n_hospitals <- length(unique(data$patient_data$hospital_id))
```

```{r}
my_paste <- function(x) {
  paste0(as.integer(x), collapse = "")
}
wide  %>% 
  arrange(hospital_id, patient_id, day) %>%
  mutate(patient_id = factor(patient_id), patient_id = fct_reorder(patient_id, breathing,  .fun = my_paste, .desc = FALSE)) %>%
  ggplot(aes(x = day, y = patient_id, fill = breathing)) + 
  geom_tile() + 
  scale_fill_viridis_d(direction = -1) +
  theme(axis.text.y = element_blank()) +
  theme(axis.title.y = element_blank(), axis.ticks.y = element_blank())

```
